\vspace{-2.25cm} Development of Ocular Disease Auxiliary Diagnosis System

### 2024-08-27 Paper/Paper.tex
Draw GradCAM highlighted figures; plot OCT acc and loss

\begin{document}
	\title{\vspace{-2.25cm} Development of Ocular Disease Auxiliary Diagnosis System}
	\author{Jerry Pan}
	\date{}
	\maketitle

@@

	\pagebreak
	\vspace{0.5cm}
	\tableofcontents
	\pagebreak

@@

@@

		Fig: OCT abnormities
		Fig: Fundus abnormities

		No real data. use the following criteria. source for criteria

@@

		Model consists of 3 parts: OCT-Model, Fundus-Model, and Diagnosis-Model. OCT-Model and Fundus-Model are collectively called the Abnormity-Models. They use the same architecture (ResNet152, flatten to 2048 features, and fc). Diagnosis Model consists of num submodels, one of which is for normal, and the other ones for each disease. each submodel first fuses output from both Abnormity-Models, then uses an fc to get final results for normal or for the disease.

		fusion: max of OCT, max of fundus, concatenate

@@

		output

@@

			Fig: overall flowchart

@@

			CycleGAN
				Fig: Intro
				Table: selection rates
				selection criteria
				Why I did not GAN Fundus

			transforms for OCT
				for train: copy, flip, randomcomb1
				for test: copy, flip, randomcomb2 -> explain truthfulness
				explain differences between train and test, OCT and fundus

@@

			intro to five-fold train/valid (reason for using this?)

			starting point of fine-tuning???????????????????????????????
			prevent overfitting

			crossentropyloss, ADAM optimizer with LR 1e-3, batchSize 16, number of epochs...
			running time

			Fig: accuracy and loss over epochs
				trainAcc, validAcc, trainLosses, validLosses
				testAcc for best weights - align below acc graph

			conda, PyTorch;
			desktop computer with Intel® Xeon® Platinum 8352V Processor, 256G of RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 48 VRAM

@@

			time per image

@@

				Table: for each abnormity:
					accuracy (only present accuracy for TOTAL)
					precision
					recall/sensitivity
					specificity
					F1
					AUC

				Table: Confusion matrix
					analyze which abnormities are commonly confused, and the effect on the numerical results
				Fig: t-SNE
					which abnormities are "close"

				Fig: ROC for each abnormity

				comparison to other studies

			"co-dominance"??????????????????????????????

			Fig: GradCAM intro
			Fig: GradCAM example

@@

			how to choose data (with an example)
			how to find grade (number of traits = grade for the disease as label during training)

@@

			parameters used
			running time
			Fig: accuracy and loss over epochs
				trainAcc, validAcc, trainLosses, validLosses

@@

			output - calculate expected grade. in order to compare, divide by total number of traits for this disease so that normalized grade falls in [0, 1].

			Table: for each disease:
				accuracy (only present accuracy for TOTAL)
				precision
				recall/sensitivity
				specificity
				F1
				AUC
			Fig: confusion matrix (is it suitable?)
			Fig: ROC for each disease

			"co-dominance"???????????????????????????????????

@@

		Do two models increase accuracy?
			how do I compare?????????????????????????????????
			any math here?

		Comparison

		Strengths and weaknesses
		how to improve

@@

	\section{Appendix}

		Google Image source links
		Add prevalence (1 out of how many people) for abnormities?

@@

		APP/website description
		GitHub repo

>>>>

\begin{document}
	\title{\vspace{-2.25cm} Development of Ocular Disease Auxiliary Diagnosis System}
	\author{Jerry Pan}
	\date{}
	\maketitle
	\vspace{0.5cm}

@@

	TEXT: abstract

	\pagebreak
	\tableofcontents
	\pagebreak

@@

		TEXT: Edit background

@@

		Fig: OCT abnormities and Fundus abnormities

		TEXT: No real data. use the following criteria. source for criteria

@@

		TEXT: Model consists of 3 parts: OCT-Model, Fundus-Model, and Diagnosis-Model. OCT-Model and Fundus-Model are collectively called the Abnormity-Models. They use the same architecture (ResNet152, flatten to 2048 features, and fc). Diagnosis Model consists of num submodels, one of which is for normal, and the other ones for each disease. each submodel first fuses output from both Abnormity-Models, then uses an fc to get final results for normal or for the disease.

		TEXT: max of OCT, max of fundus, concatenate; concatenate D1 outputs

@@

		TEXT: output

@@

			Fig: preparation flowchart (include cycleGAN)

@@

			TEXT: CycleGAN
				Table: selection rates
				selection criteria
				Why I did not GAN Fundus

			TEXT: transforms for OCT
				for train: copy, flip, randomcomb1
				for test: copy, flip, randomcomb2 -> explain truthfulness
				explain differences between train and test, OCT and fundus

@@

			TEXT: intro to five-fold train/valid (reason for using this?)

			TEXT: starting point of fine-tuning???????????????????????????????
			prevent overfitting

			TEXT: crossentropyloss, ADAM optimizer with LR 1e-3, batchSize 16, number of epochs...
			conda, PyTorch;
			desktop computer with Intel® Xeon® Platinum 8352V Processor, 256G of RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 48 VRAM

			Graph: accuracy and loss over epochs
			TEXT: comments

@@

@@

				TEXT: accuracy; explain top-probs method

				Table: for each abnormity:
					precision
					recall/sensitivity
					specificity
					F1
					AUC

				Graph: Confusion matrix
				TEXT: analyze which abnormities are commonly confused, and the effect on the numerical results
				Graph: t-SNE
				TEXT: which abnormities are "close"

				Graph: ROC for each abnormity

				TEXT: comparison to other studies

			Fig: GradCAM example

@@

			TEXT: how to choose data (with an example)
			how to find level (number of traits = level for the disease as label during training)

@@

			TEXT: hyperparameters, software, hardware

			Graph: accuracy and loss over epochs
			TEXT: comments

@@

			TEXT: D1 output - calculate expected grade. in order to compare, divide by total number of traits for this disease so that normalized grade falls in [0, 1]. 
			used for checking number of abnormities associated to the disease

			TEXT: top-probs method

			Table: for each disease:
				precision
				recall/sensitivity
				specificity
				F1
				AUC
			Graph: D1 acc bar chart (with D2 no use-top-probs and D2 use-top-probs)
			Graph: D1 confusion matrix
			TEXT: comments

			Graph: D2 confusion matrix
			Graph: D2 tSNE
			TEXT: comments

			Graph: D2 ROC for each disease
			TEXT: comparison and comments

@@

		TEXT: Do two models increase accuracy? How?

		TEXT: Comparison to other studies

		TEXT: Strengths and weaknesses
		how to improve

@@

		TEXT: conclusion

	\pagebreak
	\section*{Appendix}

	List: Google Image source links

	Table: abnormities with description (edit the two tables below)

@@

	Fig: website
	TEXT: APP/website description

	Link: GitHub repo
